Benchmark!!1

### 2020-12-28 paper/main.tex
documentation of language differences in espprc and storing visited customers

\section{Other notes}
On the ESPPRC benchmark, a label needs to store information about
which customers have already been visited in the partial path it
represents. In Python, preliminary testing reveals that using a set of
integers for that purpose is twice as fast as using a vector of booleans.

>>>>

\section{Other notes}
On the ESPPRC benchmark, a label needs to store information about
which customers have already been visited in the partial path it
represents. In Python, preliminary testing reveals that using a set of
integers for that purpose is twice as fast as using a vector of
booleans. Similar preliminary testing in C++ reveals the opposite:
using an array of booleans is faster. This is the behaviour we would
expect in general, the observation on Python are the surprising ones
here. There are two reasons for this expectation: (i) copying an array,
represented in contiguous memory, can in general be performed faster
than copying a set structure and (ii) lookup in an array is performed
in $\cal{O}(1)$ time while lookup in a set is performed in $\cal{O}(log(n)$.
